### 2018-02-28 tex/paper.tex
progress in writing, but needs clarification in Semantics.hs before do more

\begin{allbluett}
step :: Commits -> State -> Contract -> OS -> (State,Contract,AS)
\end{allbluett}

@@

\begin{allbluett}
data Contract =
   Null |
   RedeemCC IdentCC Contract |
   RevealCV IdentCV Contract |
   Pay Person Person Int Contract |
   Both Contract Contract |
   Choice Observation Contract Contract |
   CommitValue IdentCV Person [Value] Contract |
   CommitCash IdentCC Person Cash Time Contract |
   When Observation Time Contract Contract
\end{allbluett}
%Originally on "Choice": \footnote{Doesn't the step function need to record what observations are made, so they can be archived in the blockchain? I don't see how your design will support doing so.}\footnote{Yes, we assume that it is part of the infrastructure of this language to record the values of *observables* that are used. However, we have chosen no to make it part of the language itself.}

@@

\begin{itemize} 
\item \bluett{Null} is the null contract; it will always be quiescent.
\item \bluett{RedeemCC idCC k} (\bluett{CC} stands for cash commitment.) For this contract to make progress, the creator of the cash commitment with identifier \bluett{idCC} is required to redeem the unspent funds in that commitment; the contract then continues as \bluett{k}. If the cash commitment with identifier \bluett{idCC} has expired, the remaining funds will be redeemed automatically by the \bluett{full\_step} function and a \bluett{ExpiredRedeem }action will be produced\footnote{How does the contract determine what actions resulted from a given step? Or is this not required?}\footnote{
If it is required, restructuring the DSL so that the result action appears as the 'value' of executing a step (using a monadic interface as described for id generation below) would be a good idea.}\footnote{We specify the actions generated by each kind of constructor; at each step the list of such actions, of type \bluett{AS}, is a component of the result.}. Using \bluett{RedeemCC} to redeem the same identifier \bluett{idCC} twice will result in the issue of a DuplicateRedeem action. Otherwise the contract is quiescent, waiting for the commitment to be redeemed or to expire.
\item  \bluett{RevealCV idCV k} (\bluett{CV} stands for value commitment.) For this contract to make progress, the creator of the value commitment with identifier \bluett{idCV} is required to reveal the value; the contract then continues as \bluett{k}. Otherwise the contract is quiescent, waiting for the value to be revealed. 
For the reveal to be valid, the value revealed must be in the vals list provided in the corresponding CommitValue constructor (the one with the same idCV). 
\item \bluett{Pay p1 p2 int k} requires that int is paid by p1 to p2, and continues as k. It uses the currency allocated by the cash commitments made by p1 that expire the earliest. This contract will result in a FailedPay action if the funds are not available; otherwise a SuccessfulPay action is generated.
\item \bluett{Both k1 k2} enforces the behaviour of both contracts k1 and k2. Because the model is stateful and produces output actions, to make a step it is necessary to execute a single step of each of  the contracts k1 and k2 in sequence: first k1 then k2.
\item \bluett{Choice obs k1 k2} behaves as either k1 or k2 depending on the (Boolean) result of obs at the time that the observation is made, k1 if it is True and k2 if False.
\item \bluett{CommitValue idCV p vals k}  For this contract to make progress, the user p is required to make a value commitment with identifier idCV; the contract then continues as k. In order for the commitment to be valid, the value must be one of the specified in the vals list. Otherwise the contract is quiescent, waiting for the value to be committed.
\item \bluett{CommitCash idCC p n timeout k}  For this contract to make progress, the user p is required to make a cash commitment of value n and timeout timeout (specified as a block number) with identifier idCC; the contract then continues as k. Otherwise the contract is quiescent, waiting for the cash to be committed. 
When the timeout is reached, the remaining funds will be redeemed automatically and a SuccessfulPay action will be issued that indicates a self-payment from the person p with the remaining funds. This is performed by the full\_step function, which wraps the step function.
\item \bluett{When obs timeout k def\_k} This contract will not progress until obs is True or until the current block number is greater than or equal to the one specified by timeout. In case the timeout applies, the contract will continue as def\_k, if the timeout does not apply and obs is True, then the contract continues as k. Otherwise the contract is quiescent.
\end{itemize}

>>>>

\begin{allbluett}
step :: Input -> State -> Contract -> OS -> (State,Contract,AS)
\end{allbluett}

@@

\begin{allbluett}
data Contract =
   Null |
   RedeemCC IdentCC Contract |
   Pay IdentPay Person Person Cash Timeout Contract |   -- CHANGED
   Both Contract Contract |
   Choice Observation Contract Contract |
   CommitCash IdentCC Person Cash Timeout Timeout Contract |   -- CHANGED
   When Observation Timeout Contract Contract    -- CHANGED
\end{allbluett}
%Originally on "Choice": \footnote{Doesn't the step function need to record what observations are made, so they can be archived in the blockchain? I don't see how your design will support doing so.}\footnote{Yes, we assume that it is part of the infrastructure of this language to record the values of *observables* that are used. However, we have chosen no to make it part of the language itself.}

@@

\begin{itemize} 
\item \bluett{Null} is the null contract; it will always be quiescent.
\item \bluett{RedeemCC idCC k} (\bluett{CC} stands for cash commitment.) For this contract to make progress, the creator of the cash commitment with identifier \bluett{idCC} is required to redeem the unspent funds in that commitment; the contract then continues as \bluett{k}. If the cash commitment with identifier \bluett{idCC} has expired, the remaining funds will be redeemed automatically by the \bluett{full\_step} function and a \bluett{ExpiredRedeem }action will be produced\footnote{How does the contract determine what actions resulted from a given step? Or is this not required?}\footnote{
If it is required, restructuring the DSL so that the result action appears as the 'value' of executing a step (using a monadic interface as described for id generation below) would be a good idea.}\footnote{We specify the actions generated by each kind of constructor; at each step the list of such actions, of type \bluett{AS}, is a component of the result.}. Using \bluett{RedeemCC} to redeem the same identifier \bluett{idCC} twice will result in the issue of a DuplicateRedeem action. Otherwise the contract is quiescent, waiting for the commitment to be redeemed or to expire.
\item \bluett{Pay p1 p2 int k} requires that int is paid by p1 to p2, and continues as k. It uses the currency allocated by the cash commitments made by p1 that expire the earliest. This contract will result in a FailedPay action if the funds are not available; otherwise a SuccessfulPay action is generated.
\item \bluett{Both k1 k2} enforces the behaviour of both contracts k1 and k2. Because the model is stateful and produces output actions, to make a step it is necessary to execute a single step of each of  the contracts k1 and k2 in sequence: first k1 then k2.
\item \bluett{Choice obs k1 k2} behaves as either k1 or k2 depending on the (Boolean) result of obs at the time that the observation is made, k1 if it is True and k2 if False.
\item \bluett{CommitCash idCC p n timeout k}  For this contract to make progress, the user p is required to make a cash commitment of value n and timeout timeout (specified as a block number) with identifier idCC; the contract then continues as k. Otherwise the contract is quiescent, waiting for the cash to be committed. 
When the timeout is reached, the remaining funds will be redeemed automatically and a SuccessfulPay action will be issued that indicates a self-payment from the person p with the remaining funds. This is performed by the full\_step function, which wraps the step function.
\item \bluett{When obs timeout k def\_k} This contract will not progress until obs is True or until the current block number is greater than or equal to the one specified by timeout. In case the timeout applies, the contract will continue as def\_k, if the timeout does not apply and obs is True, then the contract continues as k. Otherwise the contract is quiescent.
\end{itemize}
